### 2016-01-12 p00-ch00-intro/intro.tex
Apply review comments to Introduction
Add a paragraph of the core contributions of the thesis

A considerable amount of research has been carried out to mix object-oriented programming languages with the actor model. 
+\TODO{Find good references.}
Language extensions, libraries, and even new programming languages are the natural outcomes of such research.
The more mainstream the language, the more research and development are available in the intersection of object orientation and actor model.
For example, \cite{actor_frameworks_jvm:agha} presents a comparative analysis of such research for Java and JVM languages.

The rapid increase of computational power added a new aspect added to create a triangle: object-oriented, actor model, and \emph{concurrency}.
Concurrency makes it harder to verify programs in terms of correctness of runtime behavior. 
+\TODO{Why concurrency makes it harder?}
Scheduling of object messages in threads of executions is one of main challenges.
In addition, in the presence of scheduling and thread interleaving, it is important that objects are able to protect their state from concurrent modifications for correctness properties.
In this thesis, we take advantage of a modelling language that aims to mix the three aspects in addition to the capabilities of formal semantics and verification.
+\TODO{Explain the gain of utilization from concurrency perspective.}

>>>>

A considerable amount of research has been carried out to mix object-oriented programming languages with the actor model~\cite{philippsen2000survey}. 
Language extensions, libraries, and even new programming languages are the natural outcomes of such research.
The more mainstream the language, the more research and development are available in the intersection of object orientation and actor model.
For example, \cite{actor_frameworks_jvm:agha} presents a comparative analysis of such research for Java and JVM languages.

The rapid increase of computational power added a new aspect added to create a triangle: object-oriented, actor model, and \emph{concurrency}.
Concurrency makes it harder to verify programs in terms of correctness of runtime behavior~\cite{Herlihy:1990:linear,johnsen:history,agha:predictive:safety}. 
Scheduling of object messages in threads of executions is one of main challenges.
In addition, in the presence of scheduling and thread interleaving, it is important that objects are able to protect their state from concurrent modifications for correctness properties.
In this thesis, we take advantage of a modelling language that aims to mix the three aspects in addition to the capabilities of formal semantics and verification.

The core contributions of this thesis target at the intersection of object 
orientation, actor model, and concurrency.
We choose Java as the main programming language and as one of the mainstream 
object-oriented languages. 
We formalize a subset of Java and its concurrency API~\cite{jsr166} to 
facilitate formal verification and reasoning about it.
We create an abstract mapping from a concurrent-object modelling language, 
ABS~\cite{johnsen2012abs}, to programming semantics of Java concurrency. 
We provide the formal semantics of the mapping and runtime properties of 
the concurrency layer including deadlines and scheduling policies.
We provide an implementation of ABS concurrency layer as a Java API library 
and framework utilizing the latest langauge additions 
in Java 8~\cite{jsr335:lambda:translation}.
We design a large-scale monitoring system as a real-world application; 
the monitoring system is built with actors and ABS concurrency 
with formal semantics of ABS composed with 
schedulability analysis~\cite{fersman2007task}.
We elaborate on the elements of this research in the following.
